Title

### 2020-12-03 documents/DraftReport.Rmd
to-dos

Write-up
- intro (amanda re-reads and checks for possible additions)
- methods/equation check: change YOTY to juv (hannah)
- results (abby/hannah)

>>>>

Write-up
- intro (amanda re-reads and checks for possible additions)
- methods/equation check: change YOTY to juv (hannah)
- simulation write-up (amelia)
- results (abby/hannah)
